\chapter{Introduction}
\hrulefill

Esports Management System is an innovative platform that will revolutionize the management and organization of esports teams, participants, tournaments, and sponsors. This system seeks to provide users with an efficient and user-friendly way to search for their preferred professional esports players.

A user-friendly interface is at the core of the Esports Management System, allowing users to seamlessly navigate and explore the realm of professional esports. With only a few clicks, users can search for potential professional athletes and teams, as well as access valuable information such as their winning records and accomplishments. This enables fans and enthusiasts to remain up-to-date on their preferred players and teams, nurturing a stronger connection within the esports community.

The Esports Management System's ability to facilitate sponsorships is a crucial feature. Numerous organizations and businesses can engage in sponsorship activities, whether for the purpose of supporting tournaments or individual athletes. The system serves as a centralized repository where the information and details of these sponsors can be efficiently stored and managed. This facilitates the sponsorship process and ensures that sponsors and the esports industry collaborate effectively.

There are specialized administrators within the Esports Management System who play crucial roles in managing and enhancing the overall experience. The social media manager is among these supervisors; he or she supervises the organization's online presence and engagement on various social media platforms. In addition, the content creator/VFX/GFX team assures the creation of visually stunning and captivating content that enhances the overall esports experience.

Dynamic features and functionalities make the Esports Management System an indispensable instrument for the esports industry. It makes it easier for fans to discover and connect with professional esports players, allowing them to remain informed and engaged. It enhances collaboration between organizations and the esports community by providing a centralized platform for sponsorship management. In addition, the system enables administrators to enhance the organization's online presence and develop visually appealing content, ensuring that all stakeholders have an engaging experience.

In the following sections, we will delve deeper into the features, functionalities, and innovative aspects of the Esports Management System, demonstrating its potential to revolutionize the management and celebration of esports teams, players, tournaments, and sponsors.

\section{Project Proposal}
This proposal for the development and implementation of an Esports Management System is presented with pleasure. This revolutionary platform seeks to transform the management and organization of esports teams, players, tournaments, and sponsors. The Esports Management System will improve the user experience, encourage community engagement, and expedite operations within the esports industry by leveraging advanced technology and comprehensive functionalities.

\subsection{Purposes}

\begin{itemize}
    \item Create an intuitive web-based platform that serves as the central hub for esports administration, catering to the requirements of teams, players, tournament organizers, and sponsors.
    \item Implement a sophisticated matching algorithm to facilitate the search and discovery of favored professional esports players, thereby enhancing the fan experience and fostering esports community connections.
    \item Provide efficient sponsorship administration capabilities, enabling organizations and businesses to support tournaments or individual athletes through sponsorship activities.
    \item Enhance the organization's online presence by supervising social media platforms and having the content creator/VFX/GFX team produce visually spectacular and engaging content.
\end{itemize}


\subsection{Methodology}

\subsubsection*{System Development:}

\begin{itemize}
    \item Conduct exhaustive investigation on the necessary requirements and features of an effective Esports Management System.
    \item  Utilize industry-standard programming languages and technologies to create a scalable and secure web-based platform.
    \item Implement a user-friendly interface with intuitive navigation in order to provide a seamless and enjoyable user experience.
\end{itemize}

\subsubsection*{ Matching Algorithm}
\begin{itemize}
    \item Collaboration with data scientists and psychologists to create a matching algorithm based on personality traits, values, and beliefs.
    \item Integrate the matching algorithm into the system to recommend professional esports players compatible with the user's preferences.
\end{itemize}

\subsubsection*{Sponsorship Management}
\begin{itemize}
    \item Create an all-encompassing sponsorship management module to facilitate collaborations between organizations and the esports industry.
    \item  Provide a centralized repository for sponsor information to facilitate communication and sponsorship efficiency.
\end{itemize}

\subsubsection*{Online Presence Enhancement}
\begin{itemize}
    \item Appoint a social media manager to supervise the organization's online presence and interact with the esports community.
    \item Appoint a social media manager to supervise the organization's online presence and interact with the esports community.
\end{itemize}

\clearpage

\section{Project Scenario}
\hrulefill
\vspace*{12pt}

A company called EsportsFTW oversees a number of gaming industry teams and competitions.This company is run by an administrator who is in charge of everything.A unique ID is used to save the admin profile in the system. It was also necessary to register other data in the system, such as an email, photo, password, and name.

There are many Managers that report to the Admin and are in charge of several specialized departments. The system keeps track of each Manager's information, including their name, email address, pay, and date of hiring.The system produced a unique Department and Manager id for them. The Finance division is exclusively managed by one Manager, who also oversees the organization's finances and ensures financial stability. Data from the finances, including account numbers and balances, are also maintained in the system. Also created by the system is an ID.

Each Manager oversees a certain team in addition to the money. The Teams profile contains information about the team, including its name, country of origin, winning streaks, and total prize money. A different Manager is given to each team, guaranteeing effective structure and collaboration. The system-generated id serves as a connection between the Manager and the Teams object.

There are a number of Players who play for each squad and represent the organization in different games. Name, photo, income, winning prize money, total hours played, phone number, and address (including nation, city, zip code, and road number) are just a few of the details that may be found in a player's profile. The URLs to the athletes' social media accounts on websites like Facebook, Instagram, Twitter, and YouTube are also available.


The organization organizes competitions that bring together teams from various video games. Data from the Tournament profile includes the name, price pool, start date, and finish date. Games like Valorant, Mobile Legends: Bang Bang (MLBB), and Rainbow Six Siege are all included in each event. Name, release date, genre, game image, publisher, platform, and pricing pool are only a few examples of the game data. Different games might be linked to each event via the game id.

EsportsFTW looks for corporate sponsorships to help pay for the teams and competitions. The company's information, including name, address, sponsoring date, and phone number. Both teams and tournaments may have several corporate sponsors, creating a many-to-many link between the data for the corporations, teams, and tournaments via the system-generated id.

A Social Media Manager is also employed by EsportsFTW to oversee the company's online presence. Information like name, image, email, date of hiring, salary, phone number, and social media links (Facebook, Instagram, Twitter, and YouTube) are all included in the profile for the Social Media Manager. The VFX/GFX and material Creator teams are under the Social Media Manager's control, and both teams are responsible for producing interesting material. Data like name, image, email, phone number, income, and address (country, city, zip code, and road number) are all included in the VFX/GFX and Content Creator profiles.

The whole organization of EsportsFTW is described in this scenario, including its administration, management structure, teams, players, coaches, competitions, sponsorships, and social media management. The database offers a thorough way to arrange and monitor all parts of the business' operations, guaranteeing efficient administration and achievement in the cutthroat world of eSports.
